\begin{thebibliography}{99}

\Bibitem{AKP-2011}
\by S.~Alexander, V.~Kapovitch, A.~Petrunin
\paper Alexandrov meets {K}irszbraun
\inbook Proceedings of the {G}\"okova {G}eometry-{T}opology {C}onference 2010
\yr 2011
\pages 88--109

\Bibitem{AKP-2024}
\by S.~Alexander, V.~Kapovitch, A.~Petrunin
\book Alexandrov geometry---foundations
\serial Graduate Studies in Mathematics
\vol 236
\publ American Mathematical Society
\publaddr Providence, RI
\yr 2024
\totalpages xvii+282

\Bibitem{ANN}
\by A.~Andoni, A.~Naor, O.~Neiman
\paper Snowflake universality of {W}asserstein spaces
\jour Ann. Sci. \'Ec. Norm. Sup\'er. (4)
\vol 51
\issue 3
\yr 2018
\pages 657--700

\Bibitem{deza-lauren}
\by M.~Deza, M.~Laurent
\book Geometry of cuts and metrics
\serial Algorithms and Combinatorics
\vol 15
\publ Springer-Verlag
\publaddr Berlin
\yr 1997
\totalpages xii+587

\Bibitem{lang-schroeder}
\by U.~Lang, V.~Schroeder
\paper Kirszbraun's theorem and metric spaces of bounded curvature
\jour Geom. Funct. Anal.
\vol 7
\issue 3
\yr 1997
\pages 535--560

\Bibitem{lebedeva-petrunin-2010}
\by N.~Lebedeva, A.~Petrunin
\paper Curvature bounded below: a~definition {\`a}~la {B}erg--{N}ikolaev
\jour Electron. Res. Announc. Math. Sci.
\vol 17
\yr 2010
\pages 122--124

\Bibitem{lebedeva-petrunin2021}
\by N.~Lebedeva, A.~Petrunin
\paper 5-point {CAT(0)} spaces after {T}etsu {T}oyoda
\jour Anal. Geom. Metr. Spaces
\vol 9
\issue 1
\yr 2021
\pages 160--166

\Bibitem{lebedeva-petrunin-2024}
\by N.~Lebedeva, A.~Petrunin
\paper Five-point {T}oponogov theorem
\jour Int. Math. Res. Not. IMRN
\issue 5
\yr 2024
\pages 3601--3624

\Bibitem{lebedeva-petrunin-zolotov}
\by N.~Lebedeva, A.~Petrunin, V.~Zolotov
\paper Bipolar comparison
\jour Geom. Funct. Anal.
\vol 29
\issue 1
\yr 2019
\pages 258--282

\Bibitem{petrunin2023}
\by A.~Petrunin
\book Pure metric geometry
\serial SpringerBriefs in Mathematics
\publ Springer
\publaddr Cham
\yr 2023
\totalpages viii+103

\Bibitem{sahovic2009}
\by V.~\v{S}ahovi\'c
\thesis Approximations of {R}iemannian manifolds with linear curvature constraints
\thesisinfo Ph.D. thesis, University of M\"unster
\yr 2009

\Bibitem{sato}
\by T.~Sato
\paper An alternative proof of {B}erg and {N}ikolaev's characterization of {$\rm CAT(0)$}-spaces via quadrilateral inequality
\jour Arch. Math. (Basel)
\vol 93
\issue 5
\yr 2009
\pages 487--490

\Bibitem{sturm}
\by K.-T.~Sturm
\paper Metric spaces of lower bounded curvature
\jour Exposition. Math.
\vol 17
\issue 1
\yr 1999
\pages 35--47

\Bibitem{toyoda}
\by T.~Toyoda
\paper An intrinsic characterization of five points in a {CAT}(0) space
\jour Anal. Geom. Metr. Spaces
\vol 8
\issue 1
\yr 2020
\pages 114--165

\Bibitem{wald}
\by A.~Wald
\paper Begr\"undung einer Koordinatenlosen Differentialgeometrie der Fl\"achen
\jour Ergebnisse eines mathematischen Kolloquiums
\vol 6
\yr 1935
\pages 24--46

\end{thebibliography}
